Univalent Universes and Completness of Reversible Programs: \\ Featherweight HoTT

### 2017-03-06 upi.tex
better figure

@@

\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.7}]]
  \draw (-3,0) ellipse (1.5cm and 3cm);
  \draw (3,2) ellipse (0.5cm and 1cm);
  \draw (3,-2) ellipse (0.5cm and 1cm);
  \node[blue,ultra thick,above] at (-3,3) {$A$};
  \node[blue,ultra thick,above] at (3,3) {$P(x)$ (fiber over $x$)};
  \node[blue,ultra thick,below] at (3,-3) {$P(y)$ (fiber over $y$)};
  \draw[fill] (-3,1.5) circle [radius=0.025];
  \draw[fill] (-3,-1.5) circle [radius=0.025];
  \draw[left,cyan,thick] (-3,1.5) -- (-3,-1.5);
  \node[above] at (-3,1.5) {$x$};
  \node[below] at (-3,-1.5) {$y$};
  \draw[fill] (3,1.5) circle [radius=0.025];
  \draw[fill] (3,2.1) circle [radius=0.025];
  \draw[fill] (3,-1.8) circle [radius=0.025];
  \node[above] at (3,1.5) {$u$};
  \node[above] at (3,2.1) {$v$};
  \node[below] at (3,-1.8) {$p_*(u)$};
  \node[left,cyan] at (-3,0) {$p$};
  \draw[->,red,dashed,ultra thick] (-3,1.5) to [out=45, in=135] (2.4,2.5);
  \draw[->,red,dashed,ultra thick] (-3,-1.5) to [out=-45, in=-135] (2.4,-2.5);
\end{tikzpicture}
\end{center}

@@

\item Take $X = \ot$ with element $\star$ and $P = \lambda \_. \ot$. The
  statement $\textit{is-univalent-fibration}~P$ reduces to
  $(\star\equiv\star)\simeq(\ot\simeq\ot)$ which is true.
\item Take $X = \ot$ and $P = \lambda \_. \zt$. The statement
  $\textit{is-univalent-fibration}~P$ reduces to
  $(\star\equiv\star)\simeq(\zt\simeq\zt)$ which is also true.
\item Take $X = \ot$. For no $P$ other than the above two instances will
  we have a univalent fibration.
\item Take $X = \bt$ with elements $\fc$ and $\tc$ and
  $P = \lambda \_. \ot$. The statement
  $\textit{is-univalent-fibration}~P$ reduces to $(\fc \equiv \tc) \simeq
  (\ot\simeq\ot)$ which is false.
\item Take $X = \bt$ with elements $\fc$ and $\tc$ and
  $P = \lambda \{ \fc \to \zt; \tc \to \ot \}$ The statement
  $\textit{is-univalent-fibration}~P$ reduces to $(\fc \equiv \tc) \simeq
  (\zt\simeq\ot)$ which is true. That is the only choice of $P$
  that works (modulo symmetry).
\item For any $n > 2$, taking $X$ as sum of $n$ copies of $\ot$ can never
  give a univalent fibration.
\end{itemize}

>>>>

\makeatletter
\tikzset{my loop/.style =  {to path={
  \pgfextra{\let\tikztotarget=\tikztostart}
%%  [looseness=100, in=60,out=120]
%%  [looseness=8,min distance=5mm, in=60,out=120]
  \tikz@to@curve@path}
  }}
\makeatletter

@@

\begin{center}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.7}]]
  \draw (-3,0) ellipse (1.5cm and 3cm);
  \draw (3,2) ellipse (0.8cm and 2cm);
  \draw (3,-2) ellipse (0.5cm and 1cm);
  \node[blue,ultra thick,above] at (-3,3) {$A$};
  \node[blue,ultra thick,above] at (3,3.9) {$P(x)$ (fiber over $x$)};
  \node[blue,ultra thick,below] at (3,-3) {$P(y)$ (fiber over $y$)};
  \draw[fill] (-3,1.5) circle [radius=0.025];
  \draw[fill] (-3,-1.5) circle [radius=0.025];
  \draw[left,cyan,thick] (-3,1.5) -- (-3,-1.5);
  \node[left] (X) at (-3,1.5) {$x$};
  \path[cyan,thick] (X) edge [loop above, looseness=8, in=40, out=140] node[above] {$q$} (X);
  \node[left] at (-3,-1.5) {$y$};
  \draw[fill] (3,-1.8) circle [radius=0.025];
  \draw[fill] (3,3) circle [radius=0.025];
  \node[above] at (3,3) {$u$};
  \draw[fill] (3,2.2) circle [radius=0.025];
  \node[below] at (3,2.2) {$q_*(u)$};
  \draw[fill] (3,1) circle [radius=0.025];
  \node[below] at (3,1) {$v$};
  \node[below] at (3,-1.8) {$p_*(u)$};
  \node[left,cyan] at (-3,0) {$p$};
  \draw[->,red,dashed,ultra thick] (-3,1.5) to [out=45, in=135] (2.2,2.5);
  \draw[->,red,dashed,ultra thick] (-3,-1.5) to [out=-45, in=-135] (2.5,-2.5);
\end{tikzpicture}
\end{center}

@@

\item Take $A = \ot$ with element $\star$ and $P = \lambda \_. \ot$. The
  statement $\textit{is-univalent-fibration}~P$ reduces to
  $(\star\equiv\star)\simeq(\ot\simeq\ot)$ which is true.
\item Take $A = \ot$ and $P = \lambda \_. \zt$. The statement
  $\textit{is-univalent-fibration}~P$ reduces to
  $(\star\equiv\star)\simeq(\zt\simeq\zt)$ which is also true.
\item Take $A = \ot$. For no $P$ other than the above two instances will
  we have a univalent fibration.
\item Take $A = \bt$ with elements $\fc$ and $\tc$ and
  $P = \lambda \_. \ot$. The statement
  $\textit{is-univalent-fibration}~P$ reduces to $(\fc \equiv \tc) \simeq
  (\ot\simeq\ot)$ which is false.
\item Take $A = \bt$ with elements $\fc$ and $\tc$ and
  $P = \lambda \{ \fc \to \zt; \tc \to \ot \}$ The statement
  $\textit{is-univalent-fibration}~P$ reduces to $(\fc \equiv \tc) \simeq
  (\zt\simeq\ot)$ which is true. That is the only choice of $P$
  that works (modulo symmetry).
\item For any $n > 2$, taking $A$ as sum of $n$ copies of $\ot$ can never
  give a univalent fibration.
\end{itemize}
